---
title: "SOP Visuals"
author: "Jim Felps"
date: "4/23/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load scripts, message=FALSE, warning=FALSE, include=FALSE}
source('./scripts/01 - import.R')
source('./scripts/02 - clean.R')
```


## S&OP Slides

- Salesforce Opportunities
- Order Entry
- Engineering Efficiency Metrics


## Salesforce Pipeline + Opportunities

```{r Salesforce Pipeline all brands, fig.align='left', fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
all_backlog_opp <- backlog_and_opportun %>%
  filter(complexity != "No Engineering",
         complexity != "Parts Order",
         !is.na(complexity),
         !is.na(bucket)) %>%
  ggplot(aes(bucket, total_tons, fill = type)) +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  labs(x = "",
       y = "Tons") +
  theme(legend.position = "bottom",
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 13),
        axis.title.y = element_text(size = 15))

all_backlog_opp

```

## Backlog + Opportunities by Brand
### Opportunity Tons Factored by probability

```{r Salesforce opportunities by Brand, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
brand_backlog_opp <- backlog_and_opportun %>%
  filter(complexity != "No Engineering",
         complexity != "Parts Order",
         !is.na(complexity),
         !is.na(bucket)) %>%
  ggplot(aes(bucket, total_tons, fill = type)) +
  geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  coord_flip() +
  facet_grid(cols = vars(brand)) +
  theme(legend.position = "bottom") +
  labs(x = "",
       y = "Tons")

brand_backlog_opp
```


# Order Entry Pipeline
Expected order entry by tons and engineering hours. 
Data from Salesforce

## Order Entry Pipeline
#### Tons factored by probability

```{r Expected close by brand, echo=FALSE, message=FALSE, warning=FALSE}
butler_oe_pipe <- opp_with_complexity %>%
  filter(brand == "BUTLER",
         close_month >= current_month &
           close_month <= floor_date(current_month + months(10), "month")) %>%
  group_by(brand, close_month) %>%
  replace_na(list(
    factored_tons = 0
  )) %>%
  summarise(tons = round(sum(factored_tons),2)) %>%
  filter(close_month != 	"2021-02-01") %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(stat = "identity", fill = bluescope_darkblue) +
  coord_flip() +
  facet_grid(cols = vars(brand)) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "2 months") +
  scale_y_continuous(labels = scales::comma, limits = c(0,30000)) +
  labs(x = "",
       y = "Tons") +
  theme(axis.title = element_text(size = 13),
        axis.text = element_text(size = 13),
        strip.text = element_text(size = 15, face = "bold"),
        strip.background = element_rect(fill = bluescope_darkblue))

vp_oe_pipe <- opp_with_complexity %>%
  filter(brand == "VP",
         close_month >= current_month &
           close_month <= floor_date(current_month + months(12), "month")) %>%
  group_by(brand, close_month) %>%
  replace_na(list(
    factored_tons = 0
  )) %>%
  summarise(tons = round(sum(factored_tons),2)) %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(stat = "identity", fill = bluescope_darkgray) +
  coord_flip() +
  facet_grid(cols = vars(brand)) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "2 months") +
  scale_y_continuous(labels = scales::comma, limits = c(0,30000)) +
  labs(x = "",
       y = "Tons",
       caption = "Data from Salesforce\nOpportunities by expected close month. Tons are factored by probability") +
  theme(axis.title = element_text(size = 13),
        axis.text = element_text(size = 13),
        strip.text = element_text(size = 15, face = "bold"),
        strip.background = element_rect(fill = bluescope_darkgray),
        plot.caption = element_text(size = 13))

brand_pipline_tons <- butler_oe_pipe | vp_oe_pipe 
brand_pipline_tons 
```

## Order Entry Hours

```{r Order Entry Eng Hrs, warning=FALSE}
butler_oe_pipe_hours <- opp_with_complexity %>%
  filter(brand == "BUTLER",
         close_month >= current_month &
           close_month <= floor_date(current_month + months(12), "month")) %>%
  group_by(brand, close_month) %>%
  replace_na(list(
    factored_tons = 0,
    factored_hours = 0
  )) %>%
  summarise(hours = round(sum(factored_hours),2)) %>%
  ggplot(aes(close_month, hours)) +
  geom_bar(stat = "identity", fill = bluescope_darkblue) +
  coord_flip() +
  facet_grid(cols = vars(brand)) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "2 months") +
  scale_y_continuous(labels = scales::comma, limits = c(0, 65000)) +
  labs(x = "",
       y = "Engineering Hours",
       title = "") +
  theme(axis.title = element_text(size = 13),
        axis.text = element_text(size = 13),
        strip.text = element_text(size = 15, face = "bold"),
        strip.background = element_rect(fill = bluescope_darkblue))

vp_oe_pipe_hours <- opp_with_complexity %>%
  filter(brand == "VP",
         close_month >= current_month &
           close_month <= floor_date(current_month + months(12), "month")) %>%
  group_by(brand, close_month) %>%
  replace_na(list(
    factored_tons = 0,
    factored_hours = 0
  )) %>%
  summarise(hours = round(sum(factored_hours),2)) %>%
  ggplot(aes(close_month, hours)) +
  geom_bar(stat = "identity", fill = bluescope_darkgray) +
  coord_flip() +
  facet_grid(cols = vars(brand)) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "2 months") +
  scale_y_continuous(labels = scales::comma, limits = c(0, 65000)) +
  labs(x = "",
       y = "Engineering Hours",
       title = "",
       caption = "Data from Salesforce\nOpportunities by expected close month. Hours are factored by probability") +
  theme(axis.title = element_text(size = 13),
        axis.text = element_text(size = 13),
        strip.text = element_text(size = 15, face = "bold"),
        strip.background = element_rect(fill = bluescope_darkgray),
        plot.caption = element_text(size = 13))

oe_pip_hours <- butler_oe_pipe_hours | vp_oe_pipe_hours
oe_pip_hours
```

# Closed and Won Opportunities, Last 13 Months


## Order Entry by Brand, Last 13 Months
```{r oe by brand total tons, message=FALSE, warning=FALSE}
# brand totals

butler_tons <- order_entry_w_complexity %>%
  filter(brand == "BUTLER",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(fill = "#0e76ad", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  facet_grid(cols = vars(brand)) +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "#0e76ad", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,15000)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "Tons")

vp_tons <- order_entry_w_complexity %>%
  filter(brand == "VP",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(fill = "#ad0e32", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  facet_grid(cols = vars(brand)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#ad0e32", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,15000)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "",
       caption = "Source: Salesforce closed and won\n opportunities, last 12 months")

brand_total_tons <- butler_tons | vp_tons
brand_total_tons
```


## Order Entry by Complexity (Tons), Last 13 Months
```{r oe by complex (tons), message=FALSE, warning=FALSE}

# tons

butler_facet <- order_entry_w_complexity %>%
  filter(brand == "BUTLER",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(fill = "#0e76ad", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "#0e76ad", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,7500)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       title = "Order Entry Tons by Complexity",
       subtitle = "Butler",
       x = "",
       y = "Tons") 


vp_facet <- order_entry_w_complexity %>%
  filter(brand == "VP",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, tons)) +
  geom_bar(fill = "#ad0e32", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#ad0e32", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,7500)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       subtitle = "VP",
       x = "",
       y = "Tons",
       caption = "Source: Salesforce closed and won\n opportunities, last 12 months") 

oe_tons_patchwork <- butler_facet / vp_facet
oe_tons_patchwork

```

## Order Entry by Complexity (Margin $/Eng Hr), Last 13 Months
```{r oe by complex (margin), message=FALSE, warning=FALSE}
# margin/eng hour

butler_facet_margin <- order_entry_w_complexity %>%
  filter(brand == "BUTLER",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, margin_per_hour)) +
  geom_bar(fill = "#0e76ad", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  #geom_text(aes(label = order_count, fontface = "bold"), stat = "identity", position = position_dodge(0.9), hjust = -1) +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#0e76ad", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,700)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "",
       #title = "Margin Dollars per Engineering Hour",
       title = "Butler")


vp_facet_margin <- order_entry_w_complexity %>%
  filter(brand == "VP",
         complexity != "No Engineering") %>%
  ggplot(aes(close_month, margin_per_hour)) +
  geom_bar(fill = "#ad0e32", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  #geom_text(aes(label = paste0("n = ",order_count), fontface = "bold"), stat = "identity", position = position_dodge(0.9), hjust = 1) +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#ad0e32", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,700)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "Margin $ per Engineering Hour",
       title = "VP",
       caption = "Source: Salesforce closed and won\n opportunities, last 12 months")

oe_margin_patchwork <- butler_facet_margin / vp_facet_margin
oe_margin_patchwork
```

## Engineering Hrs/Ton - New Order Previous 13 Months
```{r oe phpt complex, message=FALSE, warning=FALSE}
butler_phpt <- order_entry_w_complexity %>%
  filter(brand == "BUTLER",
         complexity != "No Engineering") %>%
  mutate(phpt = round(eng_hours/tons,2)) %>%
  ggplot(aes(close_month, phpt)) +
  geom_bar(fill = "#0e76ad", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  #geom_text(aes(label = order_count, fontface = "bold"), stat = "identity", position = position_dodge(0.9), hjust = -1) +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#0e76ad", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,5.5)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "",
       #title = "Margin Dollars per Engineering Hour",
       title = "Butler")

vp_phpt <- order_entry_w_complexity %>%
  filter(brand == "VP",
         complexity != "No Engineering") %>%
  mutate(phpt = round(eng_hours/tons,2)) %>%
  ggplot(aes(close_month, phpt)) +
  geom_bar(fill = "#ad0e32", stat = "identity") +
  geom_smooth(method = "loess",se = FALSE, color = "black") +
  #geom_text(aes(label = paste0("n = ",order_count), fontface = "bold"), stat = "identity", position = position_dodge(0.9), hjust = 1) +
  facet_grid(cols = vars(complexity), labeller = labeller(complexity = oe_labels)) +
  theme(panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 13),
        strip.background = element_rect(fill = "#ad0e32", colour = "black"),
        strip.text = element_text(face = "bold", color = "white", size = 12),
        axis.text = element_text(size = 11),
        axis.text.x = element_text(angle = -45)) +
  scale_y_continuous(limits = c(0,5.5)) +
  scale_x_date(date_labels = "%b%y", date_breaks = "2 months") +
  labs(fill = "",
       x = "",
       y = "Engineering Hours per Ton",
       title = "VP",
       caption = "Source: Salesforce closed and won\n opportunities, last 12 months")

oe_phpt_patchwork <- butler_phpt / vp_phpt
oe_phpt_patchwork
```


## Engineering Utilization
```{r eng utilization, message=FALSE, warning=FALSE}
bbna_util <- mbr_chart_metrics_all %>%
  group_by(Org, fiscal_year, period) %>%
  summarise(util_hours = round(sum(Utilized_Hrs),2),
            hours = round(sum(Total_Hrs),2)) %>%
  mutate(utilization = round(util_hours/hours,2)) %>%
  ggplot(aes(x = period, y = utilization, fill = fiscal_year)) + 
  geom_bar(stat = "Identity", position = "dodge") +
  geom_hline(aes(yintercept = 0.7), color = "#990000", linetype = "dashed") +
  geom_text(aes(label = utilization), vjust = text_vjust, size = text_label_size, position = position_dodge(0.9)) +
  scale_fill_manual(values = custom_palette) +
  labs(title = "Employee Utilization",
       subtitle = "BBNA Engineering") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5, size = title_text),
        plot.subtitle = element_text(hjust = 0.5, size = subtitle_text),
        strip.text = element_blank(),
        legend.text = element_text(size = legend_text),
        legend.title = element_blank(),
        legend.position = "top",
        legend.direction = "horizontal",
        panel.background = element_rect(fill = bluescope_lightgray),
        panel.grid = element_line(color = bluescope_lightgray),
        axis.text = element_text(size = legend_text))

bbna_util
```

## Actual vs Quote Hours
```{r Act vs Quote Eng Hours, message=FALSE, warning=FALSE}
bbna_avq_hrs <- mbr_chart_metrics_all %>%
  group_by(Org, fiscal_year, period) %>%
  summarise(a_hours = round(sum(A_Hrs),2),
            sold_hrs = round(sum(Sold_Hrs),2)) %>%
  mutate(AvQ_Hrs = round(a_hours/sold_hrs,2)) %>%
  ggplot(aes(x = period, y = AvQ_Hrs, fill = fiscal_year)) + 
  geom_bar(stat = "Identity", position = "dodge") +
  geom_hline(aes(yintercept = 1.14), color = "#990000", linetype = "dashed") +
  geom_text(aes(label = AvQ_Hrs), vjust = text_vjust, size = text_label_size, position = position_dodge(0.9)) +
  scale_fill_manual(values = custom_palette) +
  labs(title = "Actual vs Quote Hours",
       subtitle = "BBNA Engineering") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5, size = title_text),
        plot.subtitle = element_text(hjust = 0.5, size = subtitle_text),
        strip.text = element_blank(),
        legend.text = element_text(size = legend_text),
        legend.title = element_blank(),
        legend.position = "top",
        legend.direction = "horizontal",
        panel.background = element_rect(fill = bluescope_lightgray),
        panel.grid = element_line(color = bluescope_lightgray),
        axis.text = element_text(size = legend_text))

bbna_avq_hrs
```

## Actual vs Quote Hours by Complexity
```{r AvQ Hrs by Complex, message=FALSE, warning=FALSE}
butler_complex <- new_oswt %>%
  filter(brand == "BUTLER") %>%
  group_by(brand, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  ggplot(aes(brand, avq_hours, color = over_hours)) +
  geom_jitter(alpha = 0.5, size = 4) +
  geom_hline(aes(yintercept = 1.14), color = "#990000", linetype = "dashed") +
  coord_flip() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.text = element_text(size = 15),
        panel.grid.major.y = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  labs(x = "",
       y = "",
       subtitle = "Butler") +
  #ggtitle("Actual vs Quoted Engineering Hours by Complexity") +
  scale_y_continuous(limits = c(0,4)) +
  scale_color_manual(values = c("#000000", "#e63505")) +
  facet_grid(rows = vars(complexity), labeller = labeller(complexity = labels_avq)) +
  geom_hline(data = butler_complex_avg, aes(yintercept = complex_mean))

vp_complex <- new_oswt %>%
  filter(brand == "VP") %>%
  group_by(brand, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  filter(project_name != "CHEVRON SHOP") %>%
  ggplot(aes(brand, avq_hours, color = over_hours)) +
  geom_jitter(alpha = 0.5, size = 4) +
  geom_hline(aes(yintercept = 1.14), color = "#990000", linetype = "dashed") +
  coord_flip() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.text = element_text(size = 15),
        panel.grid.major.y = element_blank(),
        strip.text = element_text(size = 15),
        plot.caption = element_text(size = 12)) +
  labs(x = "",
       y = "",
       subtitle = "VP ",
       caption = "orange dots represent jobs over complexity ceiling hours.\nRed dashed line is overall historical average of 1.14") +
  #ggtitle("Actual vs Quoted Engineering Hours by Complexity") +
  scale_y_continuous(limits = c(0,4)) +
  scale_color_manual(values = c("#000000", "#e63505")) +
  facet_grid(rows = vars(complexity), labeller = labeller(complexity = labels_avq)) +
  geom_hline(data = vp_complex_avg, aes(yintercept = complex_mean))

brand_by_complex <- butler_complex | vp_complex
brand_by_complex

financial_impact_table %>%
  kable(caption = "Financial Impact of Actual vs Quote over 1.14 Goal") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 20, stripe_color = "black")
```

```{r excel tables of projects, message=FALSE, warning=FALSE, include=FALSE}
butler_table <- new_oswt %>%
  filter(brand == "BUTLER") %>%
  group_by(brand, region, builder_name, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  select(brand, complexity, region, builder_name, project_name, avq_hours) %>%
  arrange(complexity, desc(avq_hours))

vp_table <- new_oswt %>%
  filter(brand == "VP") %>%
  group_by(brand, region, builder_name, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  select(brand, complexity, region, builder_name, project_name, avq_hours) %>%
  arrange(complexity, desc(avq_hours))

write_xlsx(butler_table, "//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/butler_table.xlsx")
write_xlsx(vp_table, "//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/vp_table.xlsx")
```


## Brand Specific Charts for MBR's

```{r}
vp_complex_only <- new_oswt %>%
  filter(brand == "VP") %>%
  group_by(brand, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  ggplot(aes(brand, avq_hours, color = over_hours)) +
  geom_jitter(alpha = 0.5, size = 4) +
  geom_hline(aes(yintercept = 1.14), color = "#990000", linetype = "dashed") +
  coord_flip() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.text = element_text(size = 15),
        panel.grid.major.y = element_blank(),
        strip.text = element_text(size = 15),
        plot.caption = element_text(size = 12)) +
  labs(x = "",
       y = "",
       title = "VP ",
       caption = "orange dots represent jobs over complexity ceiling hours.\nRed dashed line is overall historical average of 1.14") +
  #ggtitle("Actual vs Quoted Engineering Hours by Complexity") +
  #scale_y_continuous(limits = c(0,4.5), breaks = c(0.5,1,1.5,2,2.5,3,3.5,4)) +
  scale_color_manual(values = c("#000000", "#e63505")) +
  facet_grid(rows = vars(complexity), labeller = labeller(complexity = labels_avq)) +
  geom_hline(data = vp_complex_avg, aes(yintercept = complex_mean))

butler_complex_only <- new_oswt %>%
  filter(brand == "BUTLER") %>%
  group_by(brand, project_name, complexity) %>%
  summarise(
    act_hours = sum(actual_hours),
    bud_hours = sum(budgeting_hours),
    avq_hours = round(act_hours/bud_hours,2)
  ) %>%
  mutate(over_hours = if_else(complexity == "CII/FT" & act_hours > 40, "Yes",
                              if_else(complexity == "Simple" & act_hours > 100, "Yes",
                                      if_else(complexity == "Moderate" & act_hours > 200, "Yes",
                                              if_else(complexity == "Complex" & act_hours > 400, "Yes",
                                                      if_else(complexity == "High Complexity" & act_hours > 800, "Yes",
                                                              if_else(complexity == "Very High Complexity" & act_hours > 1000, "Yes", "No"))))))) %>%
  ggplot(aes(brand, avq_hours, color = over_hours)) +
  geom_jitter(alpha = 0.5, size = 4) +
  geom_hline(aes(yintercept = 1.14), color = "#990000", linetype = "dashed") +
  coord_flip() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.text = element_text(size = 15),
        panel.grid.major.y = element_blank(),
        strip.text = element_text(size = 15),
        plot.caption = element_text(size = 12)) +
  labs(x = "",
       y = "",
       title = "Butler ",
       caption = "orange dots represent jobs over complexity ceiling hours.\nRed dashed line is overall historical average of 1.14") +
  #ggtitle("Actual vs Quoted Engineering Hours by Complexity") +
  #scale_y_continuous(limits = c(0,4.5), breaks = c(0.5,1,1.5,2,2.5,3,3.5,4)) +
  scale_color_manual(values = c("#000000", "#e63505")) +
  facet_grid(rows = vars(complexity), labeller = labeller(complexity = labels_avq)) +
  geom_hline(data = butler_complex_avg, aes(yintercept = complex_mean))

financial_impact_table %>%
  select(-BUTLER) %>%
  kable(caption = "Financial Impact of Actual vs Quote over 1.14 Goal") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 20, stripe_color = "black")

financial_impact_table %>%
  select(-VP) %>%
  kable(caption = "Financial Impact of Actual vs Quote over 1.14 Goal") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 20, stripe_color = "black")
vp_complex_only
butler_complex_only


```


```{r save graphs, message=FALSE, warning=FALSE, include=FALSE}
ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/all_backlog_opp.png", all_backlog_opp, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/brand_backlog_opp.png", brand_backlog_opp, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/brand_pipline_tons.png", brand_pipline_tons, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/oe_pip_hours.png", oe_pip_hours, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/brand_total_tons.png", brand_total_tons, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/oe_tons_patchwork.png", oe_tons_patchwork, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/oe_margin_patchwork.png", oe_margin_patchwork, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/oe_phpt_patchwork.png", oe_phpt_patchwork, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/bbna_util.png", bbna_util, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/bbna_avq_hrs.png", bbna_avq_hrs, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/brand_by_complex.png", brand_by_complex, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/vp_complex_only.png", vp_complex_only, width = 16, height = 9, dpi = "retina")

ggsave("//bmkc1alfin/Fin-Acct/1 - Personal Folders/Jimbo/S&OP/charts/butler_complex_only.png", butler_complex_only, width = 16, height = 9, dpi = "retina")

```

